04_DESeq_sexes

### 2019-11-10 analysis/04_DESeq2_sexes.Rmd
fewere wgcna plots

# ceate new variable for hypothesis testing
c.colData <- c.colData %>%
    mutate(hypothesis = fct_recode(treatment,
                            "anticipation" = "control",
                            "anticipation" = "bldg",
                            "incubation" = "lay",
                            "incubation" = "inc.d3",
                            "incubation" = "inc.d9",
                            "incubation" = "inc.d17",
                            "hatchling.care" = "hatch",
                            "hatchling.care" = "n5",
                            "hatchling.care" = "n9"))

@@

```{r wgcna, eval = T, fig.width=6, fig.height=6}
# pitutiary expression

plotWGCNAcandidates(vsd.pit, c("NP_990797.2"), colDataPit, "PRL expression, Pituitary")
plotWGCNAcandidates(vsd.pit, c("NP_001090992.1"), colDataPit, "VIP1R expression, Pituitary")
plotWGCNAcandidates(vsd.pit, c("NP_990797.2", "NP_001090992.1"), colDataPit, "PRL & VIP1R expression, Pituitary")
plotWGCNAcandidates(vsd.pit, c("NP_990136.1", "NP_001035179.1"), colDataPit, "TH & AR expression, Pituitary")
plotWGCNAcandidates(vsd.pit, c("NP_990797.2", "NP_001090992.1","NP_990136.1", "NP_001035179.1", "NP_001026269.1"), 
                    colDataPit, "PRL, PRLR, VIP1R, POMC, TH & AR expression, Pituitary")
plotWGCNAcandidates(vsd.pit, c("XP_015155078.1", "XP_015146451.1", "NP_001025709.2", "NP_990327.2"), 
                    colDataPit, "Stat and JAK proteins, Pituitary")
plotWGCNAcandidates(vsd.pit,
                    c("NP_990797.2","NP_001004392.2", "NP_001004403.1", "NP_001006255.2", "NP_001006274.1",
                           "NP_989500.1", "XP_001234815.2", "XP_015149152.1", "XP_416110.5"),
                    colDataPit, "9 of 102 genes in a WGCNA module containting Prolactin")
plotWGCNAcandidates(vsd.pit,
                    c("XP_428110.3","NP_001004392.2",  "XP_015142961.1", "XP_015139636.1",
                      "XP_015137408.1", "XP_004938696.1", "NP_990620.1", "NP_001170793.2", "NP_001026250.1"),
                    colDataPit, "Prolaction receptor: 9 of 147 genes in a WGCNA module containting PRLR")
plotWGCNAcandidates(vsd.pit, c("NP_989957.1", "NP_001120784.1", "NP_001120786.1",
                               "NP_001131120.1", "NP_001186037.1", "NP_989871.1",
                               "NP_990797.2", "XP_015132722.1"), colDataPit, "Pitutary: CISH, SOCS, PRL, PRLR")

# genes from https://link.springer.com/article/10.1007%2Fs12079-012-0168-0
# A pathway map of prolactin signaling
# PL, RAC1, IRS2 not found
plotWGCNAcandidates(vsd.pit, c("NP_990797.2", "XP_015132722.1", "NP_989690.1",
                               "NP_001025709.2", "XP_015144878.1", "NP_989481.1",
                               "NP_001186467.1", "NP_990386.1", "XP_015132490.1",
                               "XP_417614.3", "XP_015150421.1", "NP_001155844.1"), 
                    colDataPit, "Pit: Genes involved in prolactin signaling")

# hyp
plotWGCNAcandidates(vsd.hyp, c("NP_989957.1", "NP_001120784.1", "NP_001120786.1",
                               "NP_001131120.1", "NP_001186037.1", "NP_989871.1",
                               "NP_990797.2", "XP_015132722.1"), colDataHyp, "Hypothalamus: CISH, SOCS, PRL, PRLR")
plotWGCNAcandidates(vsd.hyp, c("NP_001170780.1", "NP_001090992.1", "NP_001014970.1"), colDataHyp, "VIP expression, Hypothalamus")

plotWGCNAcandidates(vsd.hyp, c("NP_990797.2", "XP_015132722.1", "NP_989690.1",
                               "NP_001025709.2", "XP_015144878.1", "NP_989481.1",
                               "NP_001186467.1", "NP_990386.1", "XP_015132490.1",
                               "XP_417614.3", "XP_015150421.1", "NP_001155844.1"), 
                    colDataHyp, "Hyp: Genes involved in prolactin signaling")

# gonad
plotWGCNAcandidates(vsd.gon, c("NP_989957.1", "NP_001120784.1", "NP_001120786.1",
                               "NP_001131120.1", "NP_001186037.1", "NP_989871.1",
                               "NP_990797.2", "XP_015132722.1"), colDataGon, "Gonad: CISH, SOCS, PRL, PRLR")

plotWGCNAcandidates(vsd.gon, c("NP_990797.2", "XP_015132722.1", "NP_989690.1",
                               "NP_001025709.2", "XP_015144878.1", "NP_989481.1",
                               "NP_001186467.1", "NP_990386.1", "XP_015132490.1",
                               "XP_417614.3", "XP_015150421.1", "NP_001155844.1"), 
                    colDataGon, "Gonad: Genes involved in prolactin signaling")

```

```{r wgcna2, eval = T, fig.width=12, fig.height=8}
PRL_associated <- read.csv("../results/08_PRL_associated.csv", header = T)
prl36 <-  PRL_associated$entrezid[1:57]
prl72 <-  PRL_associated$entrezid[58:102]
plotWGCNAcandidates(vsd.pit, prl36, colDataPit, "A-K genes with PRL pattern in the pituitary")
plotWGCNAcandidates(vsd.pit, prl72, colDataPit, "K-Z genes with PRL pattern in the pituitary")

PRLR_associated <- read.csv("../results/08_PRLR_associated.csv", header = T)
prlr36 <-  PRLR_associated$entrezid[1:57]
prlr72 <-  PRLR_associated$entrezid[58:115]
prlr116<-  PRLR_associated$entrezid[116:147]
plotWGCNAcandidates(vsd.pit, prlr36, colDataPit, "A-G genes with PRLR pattern in the pituitary")
plotWGCNAcandidates(vsd.pit, prlr72, colDataPit, "L-S genes with PRLR pattern in the pituitary")
plotWGCNAcandidates(vsd.pit, prlr116, colDataPit, "S-Z genes with PRLR pattern in the pituitary")

VIPR1_associated <- read.csv("../results/08_VIPR1_associated.csv", header = T)
vipr156 <-  VIPR1_associated$entrezid[398:456]
plotWGCNAcandidates(vsd.pit, vipr156, colDataPit, "Genes with VIPR1 pattern in the pituitary")

AR_associated <- read.csv("../results/08_AR_associated.csv", header = T)
AR <-  AR_associated$entrezid[1:31]
plotWGCNAcandidates(vsd.pit, AR, colDataPit, "Genes with AR pattern in the pituitary")

POMC_associated <- read.csv("../results/08_POMC_associated.csv", header = T)
pomc <-  POMC_associated$entrezid[32:61]
plotWGCNAcandidates(vsd.pit, pomc, colDataPit, "Genes with POMC pattern in the pituitary")

```

```{r topPCAloadings}
# COX1, COX3, CHGA, PRL, ATP2B4, LOC107055658
topPCAloadings <- c("NP_006917.1", "NP_006921.2","XP_421330.1", "NP_990797.2", "XP_015154447.1", "XP_015156300.1")

plotWGCNAcandidates(vsd.hyp, topPCAloadings, colDataHyp, "Hypothalamus")
plotWGCNAcandidates(vsd.pit, topPCAloadings, colDataPit, "Pituitary")
plotWGCNAcandidates(vsd.gon, topPCAloadings, colDataGon, "Gonads")

```

>>>>

# ceate new variable for hypothesis testing
c.colData <- c.colData %>%
    mutate(hypothesis = fct_recode(treatment,
                            "non-parental" = "control",
                            "non-parental" = "bldg",
                            "incubation" = "lay",
                            "incubation" = "inc.d3",
                            "incubation" = "inc.d9",
                            "incubation" = "inc.d17",
                            "hatchling.care" = "hatch",
                            "hatchling.care" = "n5",
                            "hatchling.care" = "n9"))

@@

```{r wgcna, eval = T, fig.width=6, fig.height=6}
# pitutiary expression
plotWGCNAcandidates(vsd.pit, c("NP_990797.2"), colDataPit, "PRL expression, Pituitary")

# COX1,  PRL, 
topPCAloadings <- c("NP_006917.1",  "NP_990797.2")
h <- plotWGCNAcandidates(vsd.hyp, topPCAloadings, colDataHyp, "Hypothalamus")
p <- plotWGCNAcandidates(vsd.pit, topPCAloadings, colDataPit, "Pituitary")

plot_grid(h + theme(axis.text.x = element_blank(), legend.position = "none"),
          p , nrow = 2, rel_heights = c(0.45,0.55))
```

```{r wgcna2, eval = T, fig.width=12, fig.height=8}
PRL_associated <- read.csv("../results/08_PRL_associated.csv", header = T)
prl36 <-  PRL_associated$entrezid[1:57]
prl72 <-  PRL_associated$entrezid[58:102]

plotWGCNAcandidates(vsd.pit, prl36, colDataPit, "A-K genes with PRL pattern in the pituitary")
plotWGCNAcandidates(vsd.pit, prl72, colDataPit, "K-Z genes with PRL pattern in the pituitary")
```
